Stable Hot Spot Analysis (Draft)

### 2017-06-14 paper-main.tex
Extended Results

Our results are based on the cab taxi dataset from New York, Manhattan \cite{TODO}. 
We used only the dataset of January 2016. From that
dataset we used the $pickup\_longitude$ and $pickup\_latitude$ column. 
The borders of the raster are between (40.699607, -74.020265) and (40.769239, -73.948286). 
Zoom size 1 means we aggregate every point, which was in range of 100x100*0.000001 into one pixel. 
In zoom size N we aggregated NxN pixel from zoom size 1 into a new pixel.
%
For our measurements we specified the following data series:
\begin{itemize}
 \item The weight matrix W is from 3 to 43 with a stepsize of 4.
 \item The focal matrix F is from  17 to 125 with a stepsize of 12.
 \item The zoom level is from 1 to 5 with a stepsize of 1.
\end{itemize}
Therefore we calculate around $10 \cdot 10 \cdot 5=500$ results for each fixed x.
The following conditions must hold F>W, F<Raster.cols und F<Raster.rows.

@@

\subsection{Results and Discussion}

% Focal size  
%	Increase of focal size leads to better results in the upward property
% 	Standard deviation decrease with higher focal size 
%	No standard deviation af F 17x17 because of missing clusters
%	The downward property reaches its maximum at 65x65
%
%	Conclusion: F should be around 65x65 or higher
In figure ~\ref{fig:fUp} you can see that an increase of the focal size leads to better results for $SoH^{\uparrow}$. 
The standard deviation decreases also with a higher focal size. Only 
at focal size F of 17x17 there is no standard deviation. At focal size F 17x17 the standard deviation is 
missing, because the weight size W must be smaller than F. When F and W have similar
size, there are no clusters. (TODO assumtion for SOH, if no clusters we asume Up/Down = 0)
$SoH^{\downarrow}$ in figure ~\ref{fig:fDown} reaches its maximum for focal size F 65x65 in the regarded area.

@@

%
% Weight size
%	Increase of weight leads to increase of downward property
%	Small break downs for G* for upward and downward property
%	For the upward property Focal G* is better than G*
%
%	Conclusion: Higher weight size leads to better results. There are parametrisations of Focal G* which are better than G*
In figure ~\ref{fig:wDown} one can see that an increase of the weight size leads to better results.
Focal $G^*$ is not allways better than $G^*$ which would be a perfect result we hoped for. But it seems 
that $G*$ has at 23 and 39 some parametrisation which leads to small break downs. 
The standard deviation is in this area higher than in the other points.
In figure ~\ref{fig:wUp} the break downs are also visible.
The high standard deviation indicates that it is possible to use this parametrisation for better results
The $SoH^{\uparrow}$ in ~\ref{fig:wUp} is mostly better than $G^*$ which was our conclusion in \ref{TODO last paper}.

\begin{figure}[htp]
  \begin{subfigure}{\linewidth}
    \caption{SoH up for weight size}
    \includegraphics[width=\linewidth]{images/whiskerPlot/wUp}
    \label{fig:wUp}
  \end{subfigure}
  \hspace{1em}
  \begin{subfigure}{\linewidth}
    \caption{SoH down for weight size}
    \includegraphics[width=\linewidth]{images/whiskerPlot/wDown}
    \label{fig:wDown}
  \end{subfigure}
  \caption{SoH for weight size}
  \label{fig:SoHWeight}
\end{figure}
%
% Zoom
%	G* alwas better than Focal G* for upward and downward property
%	Focal G* has different focal sizes because zoom is compared
%	At zoom level 4 G* increase much more than Focal G*
%
%	Conclusion: G* is better than Focal G* in the zoom dimension, but the focal size is fixed. The zoom dimension has the least 
%	influence on the value
The last variation we examined was the zoom level. The results can seen in figure ~\ref{fig:SoHZoom}. One can see that $G^*$ is always better than Focal $G^*$.
The target area of Focal $G^*$ increases with every zoom step.

>>>>

Our results are based on the cab taxi dataset from New York, Manhattan \cite{TODO}. 
We used only the dataset of January 2016. From that
dataset we used the $pickup\_longitude$ and $pickup\_latitude$ column. 
The borders of the raster are between (40.699607, -74.020265) and (40.769239, -73.948286). 
Zoom size 1 means we aggregate every point, which was in range of $100x100 \cdot 0.000001$ into one pixel. 
In zoom size N we aggregated NxN pixel from zoom size 1 into a new pixel.
%
For our measurements we specified the following data series:
\begin{itemize}
 \item The weight matrix W is from 3 to 43 with a stepsize of 4.
 \item The focal matrix F is from  17 to 125 with a stepsize of 12.
 \item The zoom level is from 1 to 5 with a stepsize of 1.
\end{itemize}
Therefore we calculate around $10 \cdot 10 \cdot 5=500$ results for each fixed x.
The following conditions must hold F>W, F<Raster.cols und F<Raster.rows.

@@

\section{Methode}

The weight size W, focal size F and the zoom level are the 3 parameters we vary.
Therefore we have a 3 dimensional space. The SoH is defined for every tuple of points.
We choose to fix one dimension and used the other dimension as our sample group. 
Out of the sample group we calculate the mean and the standard deviation. 
In our graph we show the mean and the standard deviation from the mean. 
We define as a child the previous image out of the fixed dimension.

\section{Results and Discussion}

% Focal size  
%	Increase of focal size leads to better results in the upward property
% 	Standard deviation decrease with higher focal size 
%	No standard deviation af F 17x17 because of missing clusters
%	The downward property reaches its maximum at 65x65
%
%	Conclusion: F should be around 65x65 or higher

First we fixed the focal size F as our x-axis. Therefore we have no $G^*$ to compare against Focal $G^*$ because $G^*$ has a fixed study area.
To evaluate this dimension is essential because if it is not known how big the study area needs to be. Based on these results we want to fix the focal size F
so that in most cases focal $G^*$ is better than $G^*$.
In figure ~\ref{fig:SoHFocal} the \SOHUP and \SOHDOWN is shwon for $G^*$ and Focal $G^*$.
Higher values mean that the found hot spots are more stable. The \SOHUP in figure ~\ref{fig:fUp} growth with an increase of the focal size.
It can see that an increase of the focal size leads to better results for \SOHUP. 
With a higher focal size you can see that the dotted line which represent the standard deviation is getting smaller.
Therefore the standard deviation decreases with a higher focal size. Only 
at focal size F of 17x17 there is no standard deviation. Which is presented with the absent of the dotted line.
At focal size F 17x17 the standard deviation is missing, because the weight size W must be smaller than F. 
And for focal size F the values for W which are caluclated are only 3,7,11.
When F and W have similar size, there are no clusters. Because the values have no much variation. (TODO assumtion for SOH, if no clusters we asume Up/Down = 0)
\SOHDOWN can also be calculated with the same images. 
\SOHDOWN in figure ~\ref{fig:fDown} reaches its maximum for focal size F 65x65 in the regarded area. The standard deviation is not decreasing with an increase of the 
focal size. Also the standard deviation is missing for the first point.

@@

%
% Weight size
%	Increase of weight leads to increase of downward property
%	Small break downs for G* for upward and downward property
%	For the upward property Focal G* is better than G*
%
%	Conclusion: Higher weight size leads to better results. There are parametrisations of Focal G* which are better than G*
Next we fixed the weight dimension as our x-axis. The values are increasing with an increase of the weight size W. 
Higher values means the results are more stable.
In figure ~\ref{fig:wUp} one can see that an increase of the weight size leads to better results forh the \SOHUP. 
We compare $G^*$ (blue line) wiht Focal $G^*$ (red line). The read line is not always above the blue line.
Therefore Focal $G^*$ is not allways better than $G^*$ which would be a perfect result we hoped for. It seems 
that $G^*$ has at 23 and 39 some small break downs. At first glance one would say that some parametrisation leads to that result
but the standard deviation is decreasing which indicate the opposite.
The standard deviation is in this area higher than in the other points.
In figure ~\ref{fig:wDown} the break downs are also visible which uses the same images as before but calculate the \SOHDOWN.
The high standard deviation in general indicates that it is possible to use better parametrisation for better results. Which would be the zoom size.
The break downs at 23 and 39 are also visible but this time the standard deviation is increasing.
The \SOHDOWN and \SOHUP is mostly better than $G^*$ with fixed x-axis for the weight. 
Which was the conclusion in \ref{TODO last paper}.

\begin{figure}[htp]
  \begin{subfigure}{\linewidth}
    \caption{SoH up for weight size}
    \includegraphics[width=\linewidth]{images/whiskerPlot/wUp}
    \label{fig:wUp}
  \end{subfigure}
  \hspace{1em}
  \begin{subfigure}{\linewidth}
    \caption{SoH down for weight size}
    \includegraphics[width=\linewidth]{images/whiskerPlot/wDown}
    \label{fig:wDown}
  \end{subfigure}
  \caption{SoH for weight size}
  \label{fig:SoHWeight}
\end{figure}
%
% Zoom
%	G* alwas better than Focal G* for upward and downward property
%	Focal G* has different focal sizes because zoom is compared
%	At zoom level 4 G* increase much more than Focal G*
%
%	Conclusion: G* is better than Focal G* in the zoom dimension, but the focal size is fixed. The zoom dimension has the least 
%	influence on the value

The last variation we examined was the zoom level. There we fixed the x-axis as our zoom level. And the focal size and weight size variation lead to a sample set.
The results can seen in figure ~\ref{fig:SoHZoom}. For the \SOHUP there is a huge increase between zoom level 3 and 4. This increase can't be seen for \SOHDOWN.
One can see that $G^*$ is always better than Focal $G^*$. This could be beacause the target area of Focal $G^*$ increases with every zoom step.
